


\documentclass[12pt,english]{article}

%\textwidth450pt \hoffset-40pt \voffset-20pt \headsep+30pt \textheight610pt
%\usepackage[margin=0.2in]{geometry}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{vmargin}
\usepackage{hyperref}
\usepackage{eurosym}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=cyan,      
    urlcolor=blue,
}
%\setmarginsrb{95pt}{70pt}{95pt}{80pt}{10pt}{10pt}{10pt}{10pt}

\usepackage{lipsum}
\newcommand\reverselabel[1]{%
  \def\theenumi{}%
  \renewcommand\makelabel{\makebox[\dimexpr\labelwidth-3pt\relax][r]{%
    \the\numexpr#1-\value{enumi}+1\relax}}}%

\begin{document}

%\footnotesize


\noindent
\begin{center}
\section*{Matteo A. Bobba} \vspace{-0.3cm}
January 2025
\end{center} 
\begin{tabular}{p{9cm}p{9cm}}
Toulouse School of Economics &  Office: T.353  \\ 
1, Esplanade de l'Universit\'{e} & Phone: +33 5 67 73 27 66\\
31080 Toulouse  &  E-mail: \href{mailto: matteo.bobba@tse-fr.eu}{matteo.bobba@tse-fr.eu} \\
France & Web: \href{https://matteobobba.github.io/}{matteobobba.github.io}  \\
\end{tabular}
\vspace{-0.1cm}
\line(1,0){450} \\
\vspace{-0.3cm}

\subsection*{Academic Positions}
Professor of Economics, Toulouse School of Economics, University of Toulouse Capitole, since September 2023. \vspace{0.2cm} \\ 
Visiting Assistant Professor and Research Scholar, Princeton University Department of Economics, 2019-2020. \vspace{0.2cm} \\
Assistant Professor, Toulouse School of Economics, University of Toulouse Capitole, 2015-2023. 

\subsection*{Professional Affiliations}
Research Fellow, Center for Economics and Policy Research (CEPR).\vspace{0.2cm} \\
Invited Researcher, Poverty Action Lab (J-PAL). \vspace{0.2cm} \\ 
Research Fellow, Institute of Labor Economics (IZA). \vspace{0.2cm} \\ 
Full Member, European Development Research Network (EUDN).

\subsection*{Other Employment}
Economist, Research Department and Vice-Presidency for Sectors and Knowledge, Inter-American Development Bank, 2011-2015. \vspace{0.2cm} \\
Research Fellow, Research Department, Inter-American Development Bank, 2005-2007.

\subsection*{Research Fields}
Labor Economics, Development Economics, Public Economics, and Policy Evaluation.

\subsection*{Education}
PhD Economics, Paris School of Economics, 2011\vspace{-0.2cm} 
\begin{itemize}
\item [--] Advisor: F. Bourguignon (PSE) \vspace{-0.3cm} 
\item [--] External Examiners: O. Attanasio (UCL) and P. Dubois (TSE). \\
\end{itemize} \vspace{-0.5cm} 
MSc Economics, Universitat Pompeu Fabra, 2005.  \vspace{0.2cm} \\
BA-BSc Economics and Statistics, Universit\'{a} Bocconi, 2004.




\subsection*{Journal Articles}
\begin{enumerate}
\reverselabel{7}
\item Enhancing Human Capital in Children. A Case Study on Scaling (with F. Agostinelli and C. Avitabile).\\ \textit{Journal of Political Economy, 2025, 133(2): 455-491.}
\item Self-Perceptions about Academic Achievement: Evidence from Mexico City (with V. Frisancho). \\
\textit{Journal of Econometrics, 2022, 231(1): 58-73}.  
\item  Labor Market Search, Informality, and Schooling Investments (with L. Flabbi and S. Levy). \\ \textit{International Economic Review, 2022, 63: 211-259}.  
\item  Labor Market Search, Informality, and On-The-Job Human Capital Accumulation (with L. Flabbi, S. Levy, and M. Tejada). \\ \textit{Journal of Econometrics, 2021, 223(2): 433-453}. 
\item Neighborhood Effects in Integrated Social Policies (with J. Gignoux). \\ \textit{World Bank Economic Review, 2019, 33(1): 116-139}.
\item Liquidity, Risk and Occupational Choices (with M. Bianchi). \\ \textit{Review of Economic Studies, 2013, 80(2): 491-511}.
\item Weak Instruments and Weak Identification in Estimating the Effects of Education on Democracy (with D. Coviello).\\ \textit{Economics Letters, 2007, 96: 301-306}.
\end{enumerate}


\subsection*{Other Publications}
\begin{enumerate}
\setcounter{enumi}{7}
\item Informality (with Gabriel Ulyssea and Lucie Gadenne). \\
\textit{VoxDevLit, 6(1), January 2023}.
\end{enumerate}

\subsection*{Working Papers}
\begin{enumerate}
\setcounter{enumi}{8}


\item Teacher Compensation and Structural Inequality: Evidence from Centralized Teacher School Choice in Peru (with T. Ederer, G. Leon, C. Neilson, and M. Nieddu).
%\\
%\textit{Reject and Resubmit, Journal of Political Economy.}
\item Perceived Ability and School Choices: Experimental Evidence and Scale-up Effects (with V. Frisancho and M. Pariguana).  

%\item High School Track Choice and Liquidity Constraints: Evidence From Urban Mexico (with C. Avitabile and M. Pariguana). 

\end{enumerate}

\subsection*{Grants and Awards}
2024: IER Top cited article 2022-2023 for ``Labor Market Search, Informality, and Schooling Investments."\vspace{0.2cm} \\
2023: JEEA Excellence in Refereeing Award.\vspace{0.2cm} \\
2015: IGC Pilot Grant (50,000 \pounds). \vspace{0.2cm} \\
2015: IDEX grant (14,000 \euro), University of Toulouse Capitole. \vspace{0.2cm} \\
2014: AFSE-Malinvaud award (best published paper among economists under age 40) for ``Liquidity, Risk and Occupational Choices". \vspace{0.2cm}\\
2008-2011: Ile-de-France, PhD scholarship. \vspace{0.2cm}\\
2004: Angelo Costa award for the best undergraduate dissertation in economics. 

\subsection*{Presentations at Seminars and Conferences}
2025: TSE Digital Conference (Discussant), Queen's Business School (scheduled). \vspace{0.2cm} \\
2024:  EUI, LMU Munich, Cologne. \vspace{0.2cm} \\
2023: NBER Development Summer Institute, Cowles Labor and Public, Y-RISE.\vspace{0.2cm} \\
2022: NBER Development Summer Institute, SITE Micro and Macro of Labor Markets,\footnote{I was invited, but co-author eventually presented as I could not attend.} MIT Dynamic Structural Econometrics, Y-RISE, Barcelona Summer Forum, TSE Departmental Seminar, WashU St Louis.\vspace{0.2cm} \\
2021: CEPR Development, CEPR Labour, BREAD, Arizona State, Cambridge, Oxford, TSE Scientific Council, RIDGE IO, WEAI.\vspace{0.2cm} \\
2020: Yale, BREAD, Econometric Society World Congress, Heriot-Watt, SEA (invited speaker). \vspace{0.2cm} \\
2019: Princeton, Cowles Structural Micro, Penn, UC San Diego, Boston University, Y-RISE, Barcelona Summer Forum, TSE Departmental Seminar, LACEA (invited speaker).\vspace{0.2cm} \\
2018: NBER Development, UCL Health and the Labor Market, WashU St Louis, Georgetown, Nova SBE, World Bank Research Group, CESifo Subjective Expectations in Economics, Agence Francaise du Developpement. \vspace{0.2cm} \\
2017: CEPR-IGC Labor and Development,\footnote{I was invited, but co-author eventually presented as I could not attend.} UCL Dynamic Structural Econometrics, Wisconsin, Tinbergen, ASSA, SOLE, IZA Labor and Development, EUDN.\vspace{0.2cm} \\
2016: IIES Stockholm, PSE, Goethe University Frankfurt, Uppsala, Bergen, TSE Departmental Seminar, IZA-SOLE Transatlantic Meeting, TSE Development Workshop, EUDN, Bordeaux-GREThA Development.\vspace{0.2cm} \\
2015:  CEPR Development, Barcelona Summer Forum, EIEF, Toulouse, Pompeu Fabra, HEC Montreal, IFS-EDePo, IDB, LACEA.  \vspace{0.2cm} \\
$<$ 2015: BREAD, Georgetown, World Bank DECRG, World Bank DIME, LACEA, NEUDC, IZA-World Bank Employment and Development, LASA, Oxford, Autonoma Barcelona, Bank of Italy, PSE, DIW, IDB, EDePo-IFS, NEUDC, Petralia Applied Economics Workshop, EUDN.  


\subsection*{Professional Service}

\noindent \underline{Referee for academic journals}: \textit{American Economic Journal: Applied, American Economic Review, Economic Journal, Economic Development and Cultural Change, Economics Letters, International Economic Review, Journal of Applied Econometrics, Journal of Development Economics, Journal of Econometrics, Journal of Economic Growth, Journal of the European Economic Association, Journal of Human Capital, Journal of Human Resources, Journal of Labor Economics, Journal of Political Economy,  Journal of Political Economy Microeconomics, Journal of Urban Economics, Labour Economics, Review of Economic Dynamics, Review of Economic Studies, World Bank Economic Review.} \\

\noindent \underline{Grant reviewer}: National Science Foundation. \\

\noindent \underline{Conferences/Workshops organization}:\\
\href{https://www.tse-fr.eu/sites/default/files/TSE/documents/sem2016/development/development_workshop_program_130616.pdf}{TSE Development Economics Workshop} (Toulouse, June 2016), Co-organizer with Emma Auriol.\vspace{0.2cm} \\
\href{https://www.tse-fr.eu/conferences/2024-economics-education-workshop}{TSE Economics of Education Workshop} (Toulouse, June 2024), Program Committee Member. \vspace{0.2cm} \\
\href{https://www.eea-esem-congresses.org/}{Econometric Society European Meetings} (Rotterdam, August 2024), Lead Coordinator for Development and Labor.\vspace{0.2cm}\\
\href{https://sites.google.com/view/iaae2025}{Annual Conference of the International Association for Applied Econometrics} (Turin, June 2025), Program Committee Member.\\


\noindent \underline{Departmental service at TSE}: \\
Head of the Thematic Group ``Behavior, Institutions, and Development'' (2024-).\vspace{0.2cm}\\
Member of the Scientific Committee of the Economics Department.\vspace{0.2cm}\\
Member of TSE Partnership Research (TSE-P). \vspace{0.2cm}\\
Junior Recruitment Committee (Member, 2017; Co-Chair, 2020).\vspace{0.2cm}\\
Organizer of the YingHua He Empirical Micro workshop (2022-).\vspace{0.2cm}\\
Organizer of the seminar series Development, Labor and Public Policy (2016-2019).


\subsection*{Teaching and Mentoring}
\underline{Graduate courses}: \\
Empirical Methods for Policy Evaluation, TSE PhD.\vspace{0.2cm} \\
Development Economics, Princeton Economics PhD.\vspace{0.2cm} \\
RCTs and Policy Evaluation, TSE Master. \vspace{0.2cm} \\
Causal Inference with Observational Data, TSE Master. \\

\noindent \underline{Undergraduate courses}: \\
Development Economics, TSE \& Princeton. \vspace{0.2cm}\\
Program Evaluation, TSE. \vspace{0.2cm}\\
Applied Econometrics, TSE. \\

\noindent \underline{PhD students advised, with initial placement ($^\star$ denotes my role as main advisor):} 
\begin{enumerate}\reverselabel{9}
\item Jonas Gathen -- Assistant Professor of Economics, Tilburg University (after Post-Doc at CEMFI).
\item Anais Fabre -- Assistant Professor of Economics, LMU Munich (after Post-Doc at the Institute for Fiscal Studies in London).
\item Tim Ederer$^\star$ -- Assistant Professor of Economics, Carnegie Mellon Tepper School of Business (after Post-Doc at UChicago, Becker-Friedman Institute).
\item Marco Pariguana (UWO) -- Early Career Researcher/Lecturer, University of Edinburgh.
\item Paloma Carrillo -- Economist, International Labor Organization.
\item Jakob Hennig -- Post-Doc, Universidad Carlos 3, Madrid,
\item Dimple Kukreja$^\star$ --  Research Economist, Reserve Bank of India.
\item Harsh Malotra$^\star$\footnote{Harsh unexpectedly and tragically passed away a few months before his thesis defense. He has been awarded the posthumous title of PhD in Economics.} 
\item Vitalijis Jascisens -- Assistant Professor of Economics, Higher Economic School.
\end{enumerate}

\subsection*{Languages}
English, Spanish, French, and Italian.

\end{document}

